---
title: "ExerciseSheet#3"
author: "Leoni Dorigatti,13013320" 
output: html_document
date: "2025-06-03"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exercise 2

### Strengths

-   Simultaneous Collaboration with other creators on the same project is possible
-   It is able to track the changes you do on your file, this way it allows you to always hop back to earlier versions.

### Weaknesses

-   You need to learn new tools
-   Multiple people working together and committing at the same time can cause confusion and problems when it comes to choosing the right changes (Merge Conflicts)

GItHub link: <https://github.com/ninid04/exeRcise-sheet-3>

## Exercise 3: Pixar Films

### a)

```{r}

# download dataset

library("tidyverse")

library(readr)

pixar_films <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2025/2025-03-11/pixar_films.csv")

# clean dataset
pixar_films <- pixar_films %>% filter(!is.na(film))

# Film rating inspection: it is a categorial variable, where "G", "PG" are values, G, stands for: General Audiance and PG, stands for Parental Guidance suggested
unique(pixar_films$film_rating)

# creat factor variable
pixar_films$film_rating <- factor(pixar_films$film_rating)

```

Reason for using factor: this variable is divided into categories and not numbers, this is important to aknowledge especially to help with analizing and grouping.

### b)

```{r}
# inspect titles
unique(pixar_films$film)

library(tidyverse)
library(stringr)

title_series <- pixar_films %>%
  filter(str_detect(film, "Toy Story|Cars|Finding|Incredibles")) %>%
  mutate(series = case_when(
    str_detect(film, "Toy Story") ~ "Toy Story",
    str_detect(film, "Cars") ~ "Cars",
    str_detect(film, "Finding") ~ "Finding",
    str_detect(film, "Incredibles") ~ "Incredibles"
  ))

# group series
summary_series<- title_series%>%
  group_by(series)%>%
  summarise(
    titles = paste(film, collapse = ", "),
    count = n()
  )

# final output
summary_series

```

### c)

```{r}
# load package
public_response <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2025/2025-03-11/public_response.csv")

# converting into factor
public_response$cinema_score <- factor(public_response$cinema_score,
        levels=c( "A-", "A", "A+"),
ordered=TRUE)

# out two datasets together
pixar_combined <- left_join(pixar_films, public_response, by="film")

```

### d)

```{r}
# creat plot for visualization of the rotten tomatoes score
pixar_combined <- pixar_combined %>%
  mutate(series = case_when(
    str_detect(film, "Toy Story") ~ "Toy Story",
    str_detect(film, "Cars") ~ "Cars",
    str_detect(film, "Finding") ~ "Finding",
    str_detect(film, "Incredibles") ~ "Incredibles",
    TRUE ~ NA_character_
  )) %>%
  filter(!is.na(series))

library(ggplot2)

ggplot(pixar_combined, aes(
  x= series,
  y= rotten_tomatoes,
  fill= film
))+ geom_bar(
  stat = "identity", 
  position = position_dodge())+ labs(
    title = "The rotten Tomatoes Score",
    subtitle = "of Pixar Film Series",
    x= "Film Series",
    y= "Rotten Tomatoes Score"
  )+ theme_light()


```

From the plot you can notice how the Rotten Tomatoes score stayed pretty consistent amongst the sequels in the series, with most of the cases slowly increasing with the second/third movies, except for 'Cars', where in the second movie, the score was way lower, almost half of compared to the other two movies. Another thing that distinguishes the 'Cars' series from the other three, is the noticeable lower 'Rotten Tomatoes Score'.

## Exercise 4: Open Analysis

### a)

```{r}
library(tidyverse)

food_waste <- read_csv("data/Food waste in the European Union - Europa (2010).csv")

```

### b)

### c)

### d) Research question

"Which 5 countries contributed the most in terms of Total Food wastage in the European Union in 2010?"

This question is interesting because it highlights the countries the contribute the most, making it possible to maybe target them and insert for example policy interventions.

### e)

```{r}
# clean data
library(janitor)

food_waste<- food_waste %>% janitor::clean_names()
food_waste_countries <- food_waste %>%
  filter(entity != "European Union")

head(food_waste)


# group country
top_5_countries <- food_waste_countries %>%
  select(entity, total_food_waste_europa_2010) %>%
  arrange(desc(total_food_waste_europa_2010)) %>%
  slice_max(total_food_waste_europa_2010, n = 5)

top_5_countries

```
The Top 5 countries in the European Union with the highest Food Waste in 2010 are: UK, Germany, Netherlands, France and Poland, with the Uk bring at the Top with a Total of 14.391.000 tonnes of wastage.

### f) Plot

```{r  fig.cap="Figure 1: Comparison of total food waste in the EU (2010) between the top 5 countries and all other countries.", out.width="80%"}
library(ggplot2)

# sum the rest of the countries food waste
other_total <- food_waste_countries %>%
  slice(6:n()) %>%
  summarise(
    total_food_waste_europa_2010 = sum(total_food_waste_europa_2010, na.rm = TRUE)
  ) %>%
  mutate(entity = "Other Countries")

# add and bind withe the top 5
combined_data <- bind_rows(top_5_countries, other_total)

# plot
ggplot(combined_data, aes(x = reorder(entity, -total_food_waste_europa_2010), y = total_food_waste_europa_2010, fill = entity)) +
  geom_col() +
  labs(
    title = "Total Food Waste in the EU (2010)",
    subtitle = "Top 5  vs All Other Countries",
    x = "Country / Group",
    y = "Total Food Waste (Tonnes)",
    fill = "Country / Group"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```
