---
title: "ExerciseSheet#3"
author: "Leoni Dorigatti,13013320" 
output: html_document
date: "2025-06-03"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Strengths

-   Simultaneous Collaboration with other creators on the same project is possible
-   It is able to track the changes you do on your file, this way it allows you to always hop back to earlier versions.

## Weaknesses

-   You need to learn new tools
-   Multiple people working together and committing at the same time can cause confusion and problems when it comes to choosing the right changes (Merge Conflicts)

# Exercise 3: Pixar Films

### a)
```{r}

# download dataset

library("tidyverse")

library(readr)

pixar_films <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2025/2025-03-11/pixar_films.csv")

# clean dataset
pixar_films <- pixar_films %>% filter(!is.na(film))

# Film rating inspection: it is a categorial variable, where "G", "PG" are values, G, stands for: General Audiance and PG, stands for Parental Guidance suggested
unique(pixar_films$film_rating)

# creat factor variable
pixar_films$film_rating <- factor(pixar_films$film_rating)

```
Reason for using factor: this variable is divided into categories and not numbers, this is important to aknowledge especially to help with analizing and grouping.

### b)
```{r}
# inspect titles
unique(pixar_films$film)

library(tidyverse)
library(stringr)

title_series <- pixar_films %>%
  filter(str_detect(film, "Toy Story|Cars|Finding|Incredibles")) %>%
  mutate(series = case_when(
    str_detect(film, "Toy Story") ~ "Toy Story",
    str_detect(film, "Cars") ~ "Cars",
    str_detect(film, "Finding") ~ "Finding",
    str_detect(film, "Incredibles") ~ "Incredibles"
  ))

# group series
summary_series<- title_series%>%
  group_by(series)%>%
  summarise(
    titles = paste(film, collapse = ", "),
    count = n()
  )

# final output
summary_series

```
### c)
```{r}
# load package
public_response <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2025/2025-03-11/public_response.csv")

# converting into factor
public_response$cinema_score <- factor(public_response$cinema_score,
        levels=c( "A-", "A", "A+"),
ordered=TRUE)

# out two datasets together
pixar_combined <- left_join(pixar_films, public_response, by="film")

```

### d)
```{r}
# creat plot for visualization of the rotten tomatoes score
pixar_combined <- pixar_combined %>%
  mutate(series = case_when(
    str_detect(film, "Toy Story") ~ "Toy Story",
    str_detect(film, "Cars") ~ "Cars",
    str_detect(film, "Finding") ~ "Finding",
    str_detect(film, "Incredibles") ~ "Incredibles",
    TRUE ~ NA_character_
  )) %>%
  filter(!is.na(series))

library(ggplot2)

ggplot(pixar_combined, aes(
  x= series,
  y= rotten_tomatoes,
  fill= film
))+ geom_bar(
  stat = "identity", 
  position = position_dodge())+ labs(
    title = "The rotten Tomatoes Score",
    subtitle = "of Pixar Film Series",
    x= "Film Series",
    y= "Rotten Tomatoes Score"
  )+ theme_light()


```
From the plot you can notice how the Rotten Tomatoes score stayed pretty consistent amongst the sequels in the series, with most of the cases slowly increasing with the second/third movies, except for 'Cars', where in the second movie, the score was way lower, almost half of compared to the other two movies. Another thing that distinguishes the 'Cars' series from the other three, is the noticeable lower 'Rotten Tomatoes Score'.
