---
title: "ExerciseSheet#3"
author: "Leoni Dorigatti,13013320" 
output: html_document
date: "2025-06-03"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Strengths

-   Simultaneous Collaboration with other creators on the same project is possible
-   It is able to track the changes you do on your file, this way it allows you to always hop back to earlier versions.

## Weaknesses

-   You need to learn new tools
-   Multiple people working together and committing at the same time can cause confusion and problems when it comes to choosing the right changes (Merge Conflicts)

# Exercise 3: Pixar Films

### a)
```{r}

# download dataset
install.packages("tidyverse")
library("tidyverse")

library(readr)

pixar_films <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2025/2025-03-11/pixar_films.csv")

# clean dataset
pixar_films <- pixar_films %>% filter(!is.na(film))

# Film rating inspection: it is a categorial variable, where "G", "PG" are values, G, stands for: General Audiance and PG, stands for Parental Guidance suggested
unique(pixar_films$film_rating)

# creat factor variable
pixar_films$film_rating <- factor(pixar_films$film_rating)

```
Reason for using factor: this variable is divided into categories and not numbers, this is important to aknowledge especially to help with analizing and grouping.

### b)
```{r}
# inspect titles
unique(pixar_films$film)

library(tidyverse)
library(stringr)

series_titles <- pixar_films %>%
  filter(str_detect(film, "Toy Story|Cars|Finding|Incredibles")) %>%
  mutate(series = case_when(
    str_detect(film, "Toy Story") ~ "Toy Story",
    str_detect(film, "Cars") ~ "Cars",
    str_detect(film, "Finding") ~ "Finding",
    str_detect(film, "Incredibles") ~ "Incredibles"
  ))
```


